---
pagetitle: "Reproducible website stack"
bibliography: packrat_bibliography.bibtex
csl: apa-custom-no-issue.csl
nocite: |
    @R @packrat @rmarkdown @knitr @formr @pander @lubridate @stringr @broom @ggplot2 @tidyr @dplyr @devtools @formatR
---

# Reproducible website stack {.tabset .tabset-sticky}

```{r message=FALSE, warning=FALSE}
source("0_helpers.R")
```

We did this cool project.

We used these [helper functions](0_helpers.html).

1. First we [wrangled the data](1_wrangle_data.html).
2. Then we looked at some [descriptives](2_descriptives.html).
3. Then we [analysed](3_analyses.html) it.

## Authors & Acknowledgements {.tabset .tabset-sticky}

### Authors
You!

This supplementary website has been archived on Zenodo.org [![DOI](https://zenodo.org/badge/xxx)](https://zenodo.org/xxx).

### Acknowledgements {.active}


#### Package bibliography {.tabset .tabset-sticky}

##### Session info (with package versions)
```{r}
# Make packrat bibliography
packrat_bibliography(overwrite_bib = TRUE, silent = TRUE)
# Turn the .R files into .Rmd files, turn those into .html, remove the .Rmd files
spin_R_files_to_site_html()
sessionInfo()
```

##### References {.active}
